Abstractions for Multi-Sorted Substitutions

### 2023-09-19 paper/paper.tex
Update.

  To fill this gap, we introduce a new abstraction that we call a
  \ACode{\ACon{ComposeKit}},
  which provides an operation \ACode{\AField{\_\&/⋯\_}} that unifies
  \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}, allowing us
  to define a general composition in the spirit of:
  \ExampleCode\KComposition

  \ACode{\ACon{ComposeKit}} and \ACode{\ADef{\_·ₖ\_}} are analogous to
  \ACode{\ACon{Kit}} and \ACode{\ADef{\_→ₖ\_}}, whereas
  \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{⋯-fusion}} are analogous to
  \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{\_⋯\_}}.

@@

@@

  Now that we have defined the \ACode{\ACon{Traversal}} structure, we
  can formulate a similar interaction between
  \ACode{\AField{wk}} and \ACode{\AField{`/id}}:
  \ExampleCode{\KIdWk}
  Shifting a variable/term \ACode{x/t} with \ACode{\AField{wk}} and then injecting
  it to a term, is the same as injecting \ACode{x/t} to a term and then applying
  a shifting renaming.

@@

>>>>

  To fill this gap, we introduce a new abstraction that we call a
  \ACode{\ACon{ComposeKit}},
  which provides an operation \ACode{\AField{\_\&/⋯\_}} that unifies
  \ACode{\ADef{\_\&\_}} and \ACode{\ADef{\_⋯\_}}. This allows us to
  define a general composition in the spirit of:
  \ExampleCode\KComposition
  We then define a \ACode{\ACon{ComposeTraversal}}, which consists of the
  \ACode{\AField{⋯-fusion}} lemma for general maps.

  Just like a \ACode{\ACon{Traversal}} allowed us to bootstrap the two
  \ACode{\ACon{Kit}} instances, the \ACode{\ACon{ComposeTraversal}} allows
  us to bootstrap the four \ACode{\ACon{ComposeKit}} instances.

  % \ACode{\ACon{ComposeKit}} and \ACode{\ADef{\_·ₖ\_}} are analogous to
  % \ACode{\ACon{Kit}} and \ACode{\ADef{\_→ₖ\_}}, whereas
  % \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{⋯-fusion}} are analogous to
  % \ACode{\ACon{ComposeTraversal}} and \ACode{\AField{\_⋯\_}}.

@@

  Before we define \ACode{\ACon{ComposeKit}} and
  \ACode{\ACon{ComposeTraversal}}, we need one more ingredient.

@@

  Now that we have defined the \ACode{\ACon{Traversal}} structure, we
  can formulate a similar interaction between
  \ACode{\AField{wk}} and \ACode{\AField{`/id}}:
  \ExampleCode{\KIdWk}
  Shifting a variable/term \ACode{x/t} with \ACode{\AField{wk}} and then injecting
  it to a term, is the same as injecting \ACode{x/t} to a term and then applying
  a shifting renaming.
  Instead of explaining \ACode{\AField{wk}} through its action on variables,
  this lemma explains \ACode{\AField{wk}} through its action on terms.

@@

  % Note that we have exactly two instances for \ACode{\ACon{Kit}}s
  % and both of them have a \ACode{\ACon{WkKit}} instance. Consequently,
  % whenever we abstract over a \ACode{\ACon{Kit}}, we can also safely assume
  % that it has a \ACode{\ACon{WkKit}} instance, without restricting the
  % lemmas usage.
